Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-02-08 WSSSPE4_report/WSSSPE4_report.tex
metrics section copied from Emily's google doc

\author{Daniel S.\ Katz$^{(1)}$,
Kyle E.\ Niemeyer$^{(2)}$,
Sandra Gesing$^{(3)}$,
Lorraine Hwang$^{(4)}$,
Alice Allen$^{(5)}$,
Jean Salac$^{(6)}$,
Neil Chue Hong$^{(7)}$,
Santiago Nunez-Corrales$^{(8)}$
Anshu Dubey$^{(9)}$,
R. Stuart Geiger$^(10)$,
Jonah Miller$^{11)}$,
Wolfgang Bangerth$^{12)}$,
Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ \note{info needed}}
%
\thanks{{}$^{(12)}$ \note{info needed}}

>>>>

\author{Daniel~S.\~Katz$^{(1)}$,
Kyle~E.\~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Alice~Allen$^{(5)}$,
Jean~Salac$^{(6)}$,
Neil~Chue~Hong$^{(7)}$,
Santiago~Nunez-Corrales$^{(8)}$
Anshu~Dubey$^{(9)}$,
R.~Stuart~Geiger$^(10)$,
Jonah~Miller$^{11)}$,
Emily~Chen$^{12)}$,
Wolfgang~Bangerth$^{13)}$,
\\Author order to be determined based on contributions
}

%
\thanks{{}$^{(1)}$ \hspace{-1ex}National Center for Supercomputing Applications (NCSA) \&
Electrical and Computer Engineering (ECE) Department \&
School of Information Sciences (iSchool),
University of Illinois at Urbana--Champaign, IL, USA; d.katz@ieee.org; ORCID: 0000-0001-5934-7525}
%
\thanks{{}$^{(2)}$ School of Mechanical, Industrial, and Manufacturing Engineering,
Oregon State University, OR, USA; kyle.niemeyer@oregonstate.edu; ORCID: 0000-0003-4425-7097}
%
\thanks{{}$^{(3)}$ \note{info needed}}
%
\thanks{{}$^{(4)}$ University of California, Davis, CA, USA; ljhwang@ucdavis.edu; ORCID: ?}
%
\thanks{{}$^{(5)}$ \note{info needed}}
%
\thanks{{}$^{(6)}$ \note{info needed}}
%
\thanks{{}$^{(7)}$ \note{info needed}}
%
\thanks{{}$^{(8)}$ \note{info needed}}
%
\thanks{{}$^{(9)}$ \note{info needed}}
%
\thanks{{}$^{(10)}$ \note{info needed}}
%
\thanks{{}$^{(11)}$ \note{info needed}}
%
\thanks{{}$^{(12)}$ \note{info needed}}
%
\thanks{{}$^{(13)}$ \note{info needed}}
